\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{ragged2e}

\input{glyphtounicode}
\setlength{\footskip}{4.08003pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tighter margins for one-page fit
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small\justifying #1
}
\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \emph{#3} & #2 \\
    \end{tabular*}\vspace{-2pt}
}
\newcommand{\resumeSubheadingCollege}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=1pt, partopsep=0pt, parsep=0pt, itemsep=0.5pt]\justifying}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newenvironment{tightItemList}{\begin{itemize}[topsep=1pt, partopsep=0pt, parsep=0pt, itemsep=0.5pt]\justifying}{\end{itemize}\vspace{-6pt}}

\begin{document}

\begin{center}
\textbf{\Huge Nikhil Singh} \\ \vspace{4pt}
\small +91 9560324262 $|$ \href{mailto:hello@semi.sh}{\underline{hello@semi.sh}} $|$
\href{https://linkedin.com/in/semi710}{\underline{linkedin.com/in/semi710}} $|$
\href{https://github.com/semi710}{\underline{github.com/semi710}} $|$
\href{https://semi.sh}{\underline{semi.sh}}
\end{center}
\vspace{-18pt}

\section{Skills}
\vspace{-8pt}
\setlength{\multicolsep}{0pt}
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.15in, label={}, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
\small{\raggedright\item{
\textbf{Languages}{: Rust, Nix (Flakes), Python (\texttt{uv}), Go, Haskell, C/C++, Bash} \\
\textbf{Systems \& Infra}{: Linux (NixOS), Kubernetes, Docker, AWS, QEMU, CI/CD} \\
\textbf{Developer Tools}{: Git, Neovim/Nixvim, Tmux, QEMU, SSH}
}}
\end{itemize}

\begin{itemize}[leftmargin=0.15in, label={}, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
\small{\raggedright\item{
\textbf{Datastores \& Messaging}{: ClickHouse, Kafka, Redis/Valkey, MySQL, MongoDB} \\
\textbf{Backend Frameworks}{: Actix Web (Rust), FastAPI, Node.js, Servant (Haskell)} \\
\textbf{Engineering Focus}{: Low-latency systems, reproducible infrastructure, distributed data pipelines}
}}
\end{itemize}
\end{multicols}
\vspace{-10pt}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Product Engineer}{Jun 2025 -- Present}
{Juspay Technologies}{Bengaluru, KA}
\resumeItemListStart
\resumeItem{Spearheaded the end-to-end architecture and development of \textbf{Project Bernoulli}, a mission-critical Rust payment gateway bridging PSPs and client SDKs, seamlessly processing 2M+ daily transactions with 99.99\% uptime.}
\resumeItem{Engineered Bernoulli's high-throughput event pipelines using \textbf{Kafka} and \textbf{ClickHouse}, optimizing SDK session management with sub-millisecond data caching via \textbf{Redis/Valkey}.}
\resumeItem{Developed the backend processing pipeline for \textbf{UDIR} (Unified Dispute and Issue Resolution) refunds, automating dispute handling and significantly accelerating merchant refund lifecycles.}
\resumeItem{Spearheaded the Nixification of the \textbf{Hyperswitch} payment router to ensure reproducible builds, and deployed a company-wide Nix devbox slashing onboarding time for 800+ engineers from hours to minutes.}
\resumeItem{Engineered the \texttt{juspay-mcp} service to orchestrate deterministic Python 3.13 environments via \texttt{uv2nix}, and deployed Nix-hosted fine-tuned LLMs, reducing manual PR reviews by 80\%.}
\resumeItem{Authored a custom GPG library in Rust with MDC payload support for secure cryptographic operations in payment flows.}
\resumeItemListEnd

\resumeSubheading
{M.Tech Researcher -- Systems Engineering}{May 2023 -- May 2025}
{Gautam Buddha University}{Greater Noida, UP}
\resumeItemListStart
\resumeItem{Authored IEEE paper on modular NixOS configurations for reproducible OS management (\href{https://ieeexplore.ieee.org/document/10991248}{IEEE Xplore}).}
\resumeItem{Co-authored IEEE paper on ML-based heavy rainfall prediction for the Northern Himalayan region.}
\resumeItem{Developed Nix flake-based configurations using disko and home-manager for hardware-agnostic deployments.}
\resumeItemListEnd

\resumeSubheading
{Software Developer Intern}{2023 -- 2024}
{Decet Technology}{Remote \& Greater Noida}
\resumeItemListStart
\resumeItem{Slashed deployment times from 2+ hours to under 5 minutes by engineering a custom Go-based CI/CD infrastructure, directly accelerating the backend release cycle.}
\resumeItem{Built core Python backend services handling 10k+ daily requests with REST APIs and database integrations.}
\resumeItemListEnd

\resumeSubheading
{Package Maintainer -- NixOS (nixpkgs) \& Arch Linux}{2020 -- Present}
{NixOS \& Arch Communities}{Remote}
\resumeItemListStart
\resumeItem{Upstreamed a highly adopted module to \texttt{home-manager}, enabling declarative user environment configurations for a large segment of the Nix community.}
\resumeItem{Maintain multiple open-source Nix flake projects and 15+ packages across \texttt{nixpkgs} and the AUR with 50k+ combined downloads; host and manage a custom binary cache.}
\resumeItem{Contributed 10+ upstream fixes to core ecosystem projects including NixOS and Hyprwm.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-10pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Ndots} $|$ \emph{NixOS System Configuration (100+ Stars)}}{2024 -- Present}
\begin{tightItemList}
\resumeItem{Modular NixOS flake orchestrating reproducible configurations across multiple personal and organizational systems, supporting diverse machine architectures.}
\resumeItem{Automated deployment pipelines integrating \texttt{sops} for secure secret management, reducing system setup time from days to under 30 minutes with full rollback capability.}
\end{tightItemList}

\resumeProjectHeading
{\textbf{Nvix} $|$ \emph{Nixvim/Neovim Distribution for Terminal Users}}{2024 -- Present}
\begin{tightItemList}
\resumeItem{Maintained a high-performance Nixvim configuration integrated with custom highlight logic, optimized for keyboard-centric workflows.}
\resumeItem{Modular plugin architecture supporting LSP, DAP, and Treesitter for 20+ languages with sub-50ms startup times.}
\end{tightItemList}

\resumeProjectHeading
{\textbf{Tmux Minimal Status} $|$ \emph{Terminal UI, Open Source}}{2020 -- Present}
\begin{tightItemList}
\resumeItem{Maintainer of popular tmux status bar (240+ GitHub stars); optimized for minimal resource footprint in high-frequency terminal environments.}
\end{tightItemList}
\resumeSubHeadingListEnd

\vspace{-12pt}
\section{Education}
\vspace{-4pt}
\resumeSubHeadingListStart
\resumeSubheadingCollege
{Gautam Buddha University}{Greater Noida, UP}
{Master of Technology in Software Engineering \textbf{(CGPA: 8.83)}}{Aug 2023 -- May 2025}
{Bachelor of Technology in Computer Science Engineering}{Aug 2020 -- Aug 2023}
\resumeSubHeadingListEnd
\end{document}
